### 2023-04-04 application.tex
details

\subsection{Regular Channel Systems}

\begin{theorem}{}
Resilience is decidable for Regular Channel Systems when $\Safe$ and $\Bad$ are regular languages.
\end{theorem}

Another proof is possible for LCS which have a (non-computable) regular reachability set. LCS are WSTS with a computable $\uparrow post^*(S)$.

corollary: Lossy Channel Systems.

 \alain{resilience decidable for LCS ? LCS sont-ils strong (quelle sémantique ?) et $\uparrow post^*(S)$ is computable ?}

>>>>

\subsection{Regular Channel Machines}

Fifo automata and systems of communicating finite-state machines (CFSMs) are essentially finite automata that communicate through fifo channels (or queues). In 1986, Pachl introduced in \cite{} the property for such systems to have a regular reachability set that gives a semi-algorithm to test non-reachability. As reachability is recursively enumerable, this provides an algorithm to solve reachability.

\begin{theorem}{}
Resilience is decidable for regular fifo automata and for systems of CFSMs when $\Safe$ and $\Bad$ are regular languages.
\end{theorem}

Since lossy channel systems have (non computable) regular reachability sets, we imediately deduce that.

\begin{corollary}
Resilience is decidable for lossy channel systems.
\end{corollary}

Another proof is possible for LCS since LCS are WSTS with a computable $\uparrow post^*(S)$.
%
 \alain{resilience decidable for LCS ? LCS sont-ils strong (quelle sémantique ?) et $\uparrow post^*(S)$ is computable ?}
